\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-15 Articles/IROS/root.tex
rewritten KERNELS AND THEIR MATRIX APPLICATIONS

Once the mapping of these points to the voxel grid is completed, we proceed to employ a specialized kernel convolution method. This method is tailored to calculate the components of the avoidance velocity vector in the Cartesian space, we generate the corresponding kernel and extract a segment of the obstacle grid of matching size, centered at agent or the point of interest (POI), resulting in two same size 3D matrices—one is a "window" from the obstacle grid $A_d$ and the other representing the kernel $K_d$.

If the agent is located near the edge of our known voxel grid we can set the eleemnts of the window would be located in the space beyond the matrix as empty in which case the robot might want to move towards this space or as occupied, which will prevent the robot from moving out of the known grid space.

By employing the Hadamard (element-wise) product (eq.~\ref{eq:hadamard}) between the cutout segment of the obstacle grid \(G_d\) and the corresponding 3D convolutional kernel \(W_d\) and than summoning all of the matrix values for each of the directions $d \in \{x, y, z\}$, we derive the resultant repulsive velocities vector \( \vec{v}_i = \left[ v_{x_i} v_{y_i} v_{z_i}\right] \).

%\begin{equation}
%	C_d = A_d \odot K_d
%	\label{eq:hadamard}
%\end{equation}

\begin{equation}
	v_d = \sum_{i,j,k} (G \odot W)_{ijk} = \sum_{i}\sum_{j}\sum_{k} g_{\Delta i \Delta j \Delta k} ~  w_{\Delta i \Delta j \Delta k}
\end{equation}

%\begin{equation}
%	\dot{x}_{poi} = \sum_{i}\sum_{j}\sum_{k} c_{dijk} 
%	\label{eq:summation}
%\end{equation}
%
%\alert{remove the above equation and add a vector of calculated velocities equation instead}
%
%\comment{}{TODO: add the indexes for x,y,z directions}

@@

\add{ADD:primer,slika}

@@

>>>>

@@

%Once the weights of the repulsive kernels have been generated, we can use kernel multiplication to get the repulsive velocity components. This method is tailored to calculate the components of the avoidance velocity vector in the Cartesian space, we generate the corresponding kernel and extract a segment of the obstacle grid of matching size, centered at agent or the point of interest (POI), resulting in two same size 3D matrices—one is a "window" from the obstacle grid $A_d$ and the other representing the kernel $K_d$.

Following the establishment of repulsive kernel weights, kernel multiplication is employed to ascertain the repulsive velocity components within Cartesian space. We select a corresponding segment from the obstacle grid, aligning in size and centered around the point of interest (POI) on the robot, where we want to calculate the repulsive velocities. This results in two identically sized 3D matrices: one serving as a "window" into the obstacle grid (\(A_d\)) and the other as the representative kernel (\(K_d\)).

%If the agent is located near the edge of our known voxel grid we can set the elements of the window would be located in the space beyond the matrix as empty in which case the robot might want to move towards this space or as occupied, which will prevent the robot from moving out of the known grid space.

Positioning of the agent at the edge of the known voxel grid necessitates a strategic decision regarding the window's boundary elements. These elements, located beyond the matrix's spatial domain, can either be considered vacant—encouraging the robot to explore these new areas—or occupied—thereby deterring the robot from exiting the mapped grid space.

%By employing the Hadamard (element-wise) product (eq.~\ref{eq:matrix-product}) between the cutout segment of the obstacle grid \(G_d\) and the corresponding 3D convolutional kernel \(W_d\) and than summoning all of the matrix values for each of the directions $d \in \{x, y, z\}$, we derive the resultant repulsive velocities vector \( \vec{v}_i = \left[ v_{x_i} v_{y_i} v_{z_i}\right] \).

Applying the Hadamard (element-wise) product to the segment of the obstacle grid \(G_d\) and the kernel \(W_d\) results in a new matrix for each Cartesian direction (\(d \in \{x, y, z\}\)). By summing over all values in this resultant matrix, we calculate the repulsive velocity component for that specific direction. This process is independently conducted for each Cartesian coordinate, ultimately yielding the comprehensive repulsive velocity vector \(\vec{v}_i = [ v_{x_i}, v_{y_i}, v_{z_i}]\).

\begin{equation}
	v_d = \sum_{i,j,k} (G \odot W)_{ijk} = \sum_{i}\sum_{j}\sum_{k} g_{\Delta i \Delta j \Delta k} ~  w_{\Delta i \Delta j \Delta k}
	\label{eq:matrix-product}
\end{equation}

%\begin{equation}
%	\dot{x}_{poi} = \sum_{i}\sum_{j}\sum_{k} c_{dijk} 
%	\label{eq:summation}
%\end{equation}
%

@@

\remove{---}
